---
title: "Curriculum Vitae"
format:
    html:
        toc: true
        page-layout: full
        include-after-body: 
            text: |
                <script src="../assets/aos.js"></script>
                <script>
                AOS.init({
                anchorPlacement: 'top-left',
                duration: 1000,
                offset: 120
                });
                </script>
    pdf:
        include-in-header: columns.tex
        geometry:
            - top=20mm
            - left=20mm
            - right=20mm
            - bottom=20mm
    docx: default
css: ../assets/cv.css
format-links: [pdf, docx]
---

```{=html}
<style>
.flushright {
   text-align: right;
   display: inline-block;
   width: 25% !important;
}

.col {
    width: 100%;
}

.rightcol {
    width: 100%;
}

.whitecol {
    width: 1% !important;
}

.cols {display: flex;}
</style>
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: load-libraries

library(httr2)
library(tibble)
library(stringr)
library(textutils)
```

::: {.print-only .contact-block}
Dr Michael Lydeamore  
Department of Econometrics and Business Statistics  
Monash University

Email: michael.lydeamore@monash.edu
:::

## {{<fa briefcase>}} Appointments Held

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Senior Lecturer - Econometrics and Business Statistics**  
Monash University

:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2021 ---
:::

::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**COVID-19 Modelling & Forecasting Lead**  
**Manager, Analytics**  
Department of Health and Human Services, Victoria

:::
::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2020
:::

::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Postdoctoral Research Fellow**  
Monash University

:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2019 --- 2021
:::

::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Honorary Team Member**  
SaferCare Victoria

:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2019 --
:::

::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Honorary Research Fellow**  
Alfred Health

:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2019 --
:::

::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Research Fellow**  
The Kirby Institute, University of New South Wales

:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2018 --- 2019
:::

::::

## {{<fa graduation-cap>}} Education

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Doctor of Philosophy -- Applied Mathematics**  
The University of Melbourne  
Thesis title: Mechanistic and statistical models of skin disease transmission

:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2015 --- 2019
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.8\textwidth}"}
**Masters of Philosophy -- Applied Mathematics**  
The University of Adelaide  
Thesis title: Approximations of stochastic household models for comparing antiviral allocation schemes  
Awarded the Applied Probability Trust prize for the highest mark with a project in Applied Mathematics and Statistics

:::

::: {.col .whitecol data-latex="{0.05\textwidth}"}
\ 
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2013 --- 2014
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Bachelor of Mathematical Sciences**  
The University of Adelaide  
Graduated with a double major in applied and pure mathematics

:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2010 --- 2013
:::
::::

## {{<fa book>}} Publications

```{r}
#| echo: false
#| results: asis


req <- request("https://api.zotero.org") |>
    req_url_query(
        v = 3,
        include = "bib",
        sort = "date",
        style = "journal-of-ecology"
    ) |>
        req_headers(`Zotero-API-Key` = Sys.getenv("ZOTERO_API_KEY")) |>
    req_url_path("users", "3027577", "publications", "items") |>
    req_retry()

resp <- req |> 
    req_perform()

a <- resp |> 
    resp_body_json() |> 
    purrr::map("bib") |> 
    unlist() |>
    #convert from HTML
    HTMLdecode() |> 
    # Convert html to markdown
    str_remove_all("<div[^>]*>") |>
    str_remove_all("<\\/div>") |> 
    #replace itallics
    str_replace_all("<\\/?i>", "*") |>
    #remove line breaks???
    str_remove_all("\\n") |>
    # Bold my name 
    str_replace("(Lydeamore, M\\.( J\\.)?)", '**\\1**') |>
    str_trim()

preprints <- a[str_count(a, pattern = "medRxiv|arxiv") > 0]
refereed <- a[!str_count(a, pattern = "medRxiv|arxiv") > 0]
```

### Preprints

```{r}
#| echo: false
#| results: asis

cat(paste0("- ", preprints), sep = "\n")
```

### Peer-reviewed articles

```{r}
#| echo: false
#| results: asis

cat(paste0("- ", refereed), sep = "\n")
```


## {{<fa money-bill>}} Funding

Almost all of this funding was obtained in partnership with large, collaborative teams.

```{r}
#| echo: false
#| message: false

funding <- tribble(
    ~title, ~organisation, ~amount, ~year,
    "Modelling Work in Low and Middle Income Counties in the Western Pacific Region for the COVID-19 SAGE Working Group", "World Health Organisation", 8157, 2024,
    "Modelling To Support Australia’s Resilience to and Preparedness for Omicron And Future Sars-Cov-2 Variants", "Commonwealth Government of Australia", 80059, 2024,
    "Contractual Partner to Conduct Research on Healthcare-Associated Infection Rates in Phillippine Hospitals", "World Health Organisation Phillippines", 72078, 2023,
    "Centre of Western Public Health Unit", "Contract Research", 25000, 2023,
    "Extending and comparing methods for projecting social contact matrices", "SPECTRUM/SPARK Seed Funding", 19438, 2022,
    "Quantifying longitudinal relationships between community mobility and COVID-19 case incidence in west metropolitan Melbourne", "SPECTRUM/SPARK Seed Funding", 19896, 2022,
    "Modelling to support Australia's national plan for COVID-19", "Commonwealth Government of Australia", 147536, 2021,
    "Modelling to support Australia's transition to 'COVID-normal'", "Australian Office of Health Protection", 25620, 2021
)

format_funding <- function(funded) {
    paste(
        ':::: {.cols data-latex=""}',
        '::: {.col data-latex="{0.85\\textwidth}"}',
        paste0('**',funded$title,'**  '),
        paste0(funded$organisation,'  '),
        paste0('Awarded value: $', scales::comma(funded$amount)),
        ':::',
        '::: {.rightcol .flushright data-latex="{0.15\\textwidth}" }',
        funded$year,
        ':::',
        '::::',
        sep = "\n"
    )
}

```

```{r}
#| echo: false
#| results: asis

formatted <- lapply(1:nrow(funding), function(i) {
    format_funding(funding[i,])
}) |> unlist()

cat(paste0(formatted), sep = "\n")
```

## <i class="bi bi-chat-quote"></i> Conference presentations and contributed talks

```{r}
#| echo: false

presentations <- tribble(
    ~title, ~extra, ~event, ~year,
    "Networks of networks in infectious diseases modelling", "Panelist", "Infectious Diseases Modelling Conference", 2024,
    "Generating synthetic contact matrices using open-source data", NA, "Australia and New Zealand Industrial Applied Mathematics Conference", 2024,
    "Data-Driven Insights into Healthcare Challenges: Two Case Studies", "Invited Speaker", "Universitätsklinikum Freiburg Seminar Series", 2023,
    "Data-Driven Insights into Healthcare Challenges: Two Case Studies", NA, "UNSW Australia Statistics & Data Science Seminar", 2023,
    "Burden of healthcare associated infections in Australia", NA, "Australia and New Zealand Industrial Applied Mathematics Conference", 2022,
    "Exponential Random Graph Models and CPE transmission", "Invited Speaker", "Melbourne Mathematical Biology Seminar Series", 2021,
    "Mathematical modelling for COVID-19 in Victoria, Australia", "Invited Speaker", "Math for Industry Forum, Vietnam", 2021,
    "The associations between transmission of CPE and ward connectivity: a network analysis", NA, "Australasian Society for Infectious Diseases Annual Scientific Meeting", 2021,
    "The burden of healthcare acquired infections in Australian public hospitals", NA, "Australasian Society for Infectious Diseases Annual Scientific Meeting", 2021,
    "Decision Making and Mathematical Biology - Victoria's usage of COVID-19 modelling", "Invited Speaker", "Mathematical Biology Special Interest Group Workshop", 2021,
    "Modelling between-household effective contact and the elimination of COVID-19 in Melbourne, Australia", NA, "Australia and New Zealand Industrial Applied Mathematics Conference", 2021,
    "Mathematical modelling and Victoria's response to COVID-19", "Invited Speaker", "Victorian ANZIAM Branch Meeting", 2020, 
    "Australia's experience and the role of modelling in its responses to COVID-19", "Invited Speaker", "Usher Institute COVID-19 Webinar", 2020,
    "Estimating epidemiological quantities for skin sores in remote Australian communities using interval-censored data", NA, "Australia and New Zealand Industrial Applied Mathematics Conference", 2019,
    "Estimating epidemiological quantities for skin sores in remote Australian communities using interval-censored data", NA, "NSW--ACT ANZIAM Branch Meeting", 2018,
    "Coupled models of Group A Streptococcus and Scabies: How likely is eradication?", NA, "PRISM International Conference", 2018,
    "Investigating the dynamics of coupled epidemiological transmission models with application to Group A Streptococcus and Scabies", NA, "Society for Mathematical Biology Annual Meeting", 2018,
    "Investigating the dynamics of coupled models with applications to Group A Streptococcus and Scabies", NA, "Australia and New Zealand Industrial Applied Mathematics Conference", 2018,
    "Quantifying the age of first infection with skin sores in five remote Australian Aboriginal communities", NA, "Lancefield International Symposium on Streptococci and Streptococcal Diseases", 2017,
    "Investigating the dynamics of coupled models with applications to Group A Streptococcus and Scabies", NA, "PRISM Annual Knowledge Transfer and Training Conference", 2017,
    "Constructing mathematical models of Group A Streptococcus and Scabies in remote Australian Indigenous communities", "Invited Speaker", "Zeeman Institute Seminar Series ", 2017,
    "Developing a model for the transmission and treatment dynamics of scabies infections a high prevalence setting", NA, "Melbourne-Manchester Joint Workshop", 2017,
    "Developing a model for the transmission of Group A Streptococcus", NA, "Australia and New Zealand Industrial Applied Mathematics Conference", 2017,
    "Determining the age of first infection from incomplete data", NA, "Modelling Emerging Infections and Neglected Tropical Diseases Workshop", 2016,
    "Investigating Intervention Intervals for Scabies Infections", NA, "Australia and New Zealand Industrial Applied Mathematics Conference", 2016
)

format_presentation <- function(presentation) {
    manipped_title <- ifelse(
        is.na(presentation$extra), 
        paste0('**',presentation$title,'**'),
        paste0('**',presentation$title,'**', " --- ", presentation$extra)
    )
    paste(
        ':::: {.cols data-latex=""}',
        '::: {.col data-latex="{0.85\\textwidth}"}',
        paste0(manipped_title,'  '),
        paste0(presentation$event,'  '),
        ':::',
        '::: {.rightcol .flushright data-latex="{0.15\\textwidth}" }',
        presentation$year,
        ':::',
        '::::',
        sep = "\n"
    )
}

```

```{r}
#| echo: false
#| results: asis

formatted <- lapply(1:nrow(presentations), function(i) {
    format_presentation(presentations[i,])
}) |> unlist()

cat(paste0(formatted), sep = "\n")
```

## {{<fa school>}} Teaching

### Lecturer

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
[ETC5513] **Reproducible and Collaborative practices** (Chief Examiner)
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2024--
:::
:::: 

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
[ETC5523] **Communicating with Data** (Chief Examiner)
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2023--
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
[ETC5512] **Wild-Caught Data**
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2022--2023
:::
:::: 

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
[ETC5521] **Exploratory Data Analysis**
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2022
:::
:::: 

### Tutor

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
[MAST10016] **Mathematics for Biomedicine**
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2016--2019
:::
:::: 

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
[MAST30001] **Stochastic Modelling**
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2018
:::
:::: 

## {{<fa award>}} Awards

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**University of Melbourne Faculty of Engineering and Information Technology Excellence Award in Interdisciplinary Research**
:::
::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2021
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**IPAA Spirit of Service Awards** -- Finalist
:::
::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2021
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Engagement Australia Excellence Awards --- Outstanding Engagement for Research Impact** --- Finalist
:::
::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2021
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Top Poster Award --- European Congress of Clinical Microbiology \& Infectious Diseases**
:::
::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2021
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**IPAA Victoria Leadership in the Public Sector Awards** --- Finalist
:::
::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2021
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Best PhD Student Presentation -- PRISM$^2$ Annual Conference**
:::
::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2017
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Applied Probability Trust Prize** for best Applied Mathematics Postgraduate Thesis
:::
::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2016
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Australian Postgraduate Award**
:::
::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2015
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Dean's Commendation for Thesis Excellence**
:::
::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2015
:::
::::


## {{<fa comments>}} Academic Service & Community Engagment

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Equity, Diversity & Social Inclusion Committee** 
Department representative
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2024 --
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**SPECTRUM Annual Meeting** 
Organising committee
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2024
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**SPARK Short Course in Mathematical Diseases Modelling** --- OUCRU   
Facilitator
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2023
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Maths in Industry Study Group** --- NSW Health  
Moderator
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2023
:::
:::: 

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**WOMBAT Communicating with Data Workshop**  
Organising Committee
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2023
:::
:::: 

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Australian and New Zealand Industrial and Applied Mathematics Executive Committee**  
Treasurer
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2022--
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Australian and New Zealand Industrial and Applied Mathematics Executive Committee**  
Early Career Representative
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2021--2022
:::
:::: 

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**SPECTRUM-SPARK Early Career Researcher Committee**  
Chair
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2022--
:::
:::: 

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**SPARK Short Course in Mathematical Diseases Modelling** -- Mahidol University  
Facilitator
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2022
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Research Tools Workshop in R**  
Facilitator
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2022
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Mathematical Biology Special Interest Group**  
Treasurer
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2019--2022
:::
:::: 

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**ANZIAM 2021 Conference**  
Organising Committee (Treasurer)
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2020--2021
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Computational Biology Research Initiative** -- The University of Melbourne  
Postgraduate Representative
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2017
:::
::::

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Computational Biology Postgraduate Sports Group** -- The University of Melbourne  
Secretary
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2017--2018
:::
:::: 

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Maths in Industry Study Group**  
Participant
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2017, 2018, 2019
:::
:::: 

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**The ConocoPhilips Science Experience** -- The University of Melbourne  
Activity Organiser
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2016--2018
:::
:::: 

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Mathematicians in Schools** -- CSIRO   
Project Supervisor/Mentor
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2016--2018
:::
::::

**Reviewer**  
PLoS Comptuational Biology; Scientific Reports; Journal of Applied Mathematics; Journal of Statistical Software; Epidemiology \& Infection; Mathematics; Medial Journal of Australia; International Tropical Health; Journal of Antimicrobial Resistance; The R Journal

## {{<fa users>}} Professional Memberships

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Australian and New Zealand Industrial and Applied Mathematics**  
Including the Mathematical Biology Special Interest Group
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2015--
:::
:::: 

:::: {.cols data-latex=""}
::: {.col data-latex="{0.85\textwidth}"}
**Australian Mathematics Society**
:::

::: {.rightcol .flushright data-latex="{0.15\textwidth}" }
2015--
:::
:::: 
 