---
title: "Curriculum Vitae"
format:
  html:
    toc: true
    page-layout: full
    include-after-body:
      text: |
        <script src="../assets/aos.js"></script>
        <script>
        AOS.init({
          anchorPlacement: 'top-left',
          duration: 1000,
          offset: 120
        });
        </script>
  typst:
    papersize: a4
    margin:
      x: 20mm
      y: 20mm
    include-in-header: cv.typ
  docx: default
css: ../assets/cv.css
format-links:
  - format: typst
    text: PDF
    icon: file-pdf
  - docx
---

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: load-libraries

library(httr2)
library(stringr)

cv_dir <- dirname(normalizePath(knitr::current_input(dir = TRUE)))
cv_data_dir <- file.path(cv_dir, "data")
source(file.path(cv_dir, "entries.R"))
```

```{r}
#| echo: false
#| results: asis
#| label: contact-details

render_contact()
```

## {{<fa briefcase>}} Appointments Held

```{r}
#| echo: false
#| results: asis

render_cv_entries("appointments.csv")
```

## {{<fa graduation-cap>}} Education

```{r}
#| echo: false
#| results: asis

render_cv_entries("education.csv")
```

## {{<fa book>}} Publications

```{r}
#| echo: false
#| results: asis
#| warning: false
#| message: false

req <- request("https://api.zotero.org") |>
  req_url_query(
    v = 3,
    include = "bib",
    sort = "date",
    style = "journal-of-ecology"
  ) |>
  req_url_path("users", "3027577", "publications", "items") |>
  req_retry()

zotero_api_key <- Sys.getenv("ZOTERO_API_KEY")
if (nzchar(zotero_api_key)) {
  req <- req |> req_headers(`Zotero-API-Key` = zotero_api_key)
}

decode_bibliography <- function(bibliography) {
  italic_open <- "QQQITALICOPENQQQ"
  italic_close <- "QQQITALICCLOSEQQQ"

  bibliography |>
    str_replace_all("<i>", italic_open) |>
    str_replace_all("</i>", italic_close) |>
    vapply(
      function(item) xml2::xml_text(xml2::read_html(paste0("<body>", item, "</body>"))),
      character(1)
    ) |>
    str_replace_all(italic_open, "*") |>
    str_replace_all(italic_close, "*")
}

resp <- req |> req_perform()

publications <- resp |>
  resp_body_json() |>
  purrr::map("bib") |>
  unlist() |>
  decode_bibliography() |>
  str_remove_all("\n") |>
  str_replace("(Lydeamore, M\\.( J\\.)?)", "**\\1**") |>
  str_replace_all("https?://[^\\s]+", function(url) paste0("<", url, ">")) |>
  str_trim()

preprints <- publications[str_count(publications, "medRxiv|arxiv|arXiv") > 0]
refereed <- publications[str_count(publications, "medRxiv|arxiv|arXiv") == 0]
```

### Preprints

```{r}
#| echo: false
#| results: asis

cat(paste0(" 1. ", preprints), sep = "\n\n")
```

### Peer-reviewed articles

```{r}
#| echo: false
#| results: asis

cat(paste0(" 1. ", refereed), sep = "\n\n")
```

## {{<fa laptop-code>}} Software

### R packages

```{r}
#| label: software
#| echo: false
#| warning: false
#| message: false
#| results: asis

library(pkgmeta)
library(stringr)
library(purrr)
library(dplyr)

extract_names <- function(author_text) {
  author_text |>
    str_remove_all("\\s*<[^>]*>|\\s*\\[[^\\]]*\\]|\\s*\\([^)]*\\)") |>
    str_split(",\\s*|\\n+") |>
    pluck(1) |>
    str_trim() |>
    paste0(collapse = ", ")
}

github_repos <- c(
  "numbats/spiderorchid"
)

cran_packages <- get_meta(cran_authors = c("Lydeamore")) |>
  mutate(
    software_source = "CRAN",
    software_url = paste0("https://CRAN.R-project.org/package=", package)
  )

github_packages <- get_meta(github_repos = github_repos) |>
  mutate(
    description = title,
    software_source = "GitHub",
    software_url = github_url
  )

packages <- bind_rows(cran_packages, github_packages) |>
  arrange(str_to_lower(package)) |>
  rowwise() |>
  mutate(authors = extract_names(authors))


for (p in seq_len(nrow(packages))) {
  software_link <- if (identical(knitr::pandoc_to(), "typst")) {
    packages$software_source[p]
  } else {
    paste0(
      "[", packages$software_source[p], "](",
      packages$software_url[p], ")"
    )
  }

  entry <- list(
    prefix = NA_character_,
    title = packages$package[p],
    title_note = NA_character_,
    role_2 = NA_character_,
    institution = NA_character_,
    detail = packages$description[p],
    detail_2 = paste0("Coauthors: ", packages$authors[p]),
    amount = NA_character_,
    date = software_link
  )

  cat(format_cv_entry(entry), "\n\n")
}
```

### VS Code extensions

```{r}
#| label: vscode-extensions
#| echo: false
#| warning: false
#| message: false
#| results: asis

openvsx <- request("https://open-vsx.org/api/-/query") |>
  req_url_query(
    namespaceName = "MichaelLydeamore",
    size = 100
  ) |>
  req_retry() |>
  req_perform() |>
  resp_body_json()

extensions <- openvsx$extensions
extensions <- extensions[order(map_chr(extensions, "displayName"))]

for (extension in extensions) {
  extension_url <- paste0(
    "https://open-vsx.org/extension/",
    extension$namespace,
    "/",
    extension$name
  )
  openvsx_link <- if (identical(knitr::pandoc_to(), "typst")) {
    "Open VSX"
  } else {
    paste0("[Open VSX](", extension_url, ")")
  }

  entry <- list(
    prefix = NA_character_,
    title = extension$displayName,
    title_note = NA_character_,
    role_2 = NA_character_,
    institution = NA_character_,
    detail = extension$description,
    detail_2 = paste0("Version ", extension$version),
    amount = NA_character_,
    date = openvsx_link
  )

  cat(format_cv_entry(entry), "\n\n")
}
```

## {{<fa money-bill>}} Funding

Almost all of this funding was obtained in partnership with large, collaborative teams.

```{r}
#| echo: false
#| results: asis

render_cv_entries("funding.csv")
```

## <i class="bi bi-chat-quote"></i> Conference presentations and contributed talks

```{r}
#| echo: false
#| results: asis

render_cv_entries("presentations.csv")
```

## {{<fa school>}} Teaching

```{r}
#| echo: false
#| results: asis

render_cv_entries("teaching.csv")
```

## {{<fa award>}} Awards

```{r}
#| echo: false
#| results: asis

render_cv_entries("awards.csv")
```

## {{<fa comments>}} Academic Service & Community Engagement

```{r}
#| echo: false
#| results: asis

render_cv_entries("service.csv")
```

**Reviewer**  
PLoS Computational Biology; Scientific Reports; Journal of Applied Mathematics; Journal of Statistical Software; Epidemiology & Infection; Mathematics; Medical Journal of Australia; International Tropical Health; Journal of Antimicrobial Resistance; The R Journal

## {{<fa users>}} Professional Memberships

```{r}
#| echo: false
#| results: asis

render_cv_entries("memberships.csv")
```
