---
title: "Curriculum Vitae"
format:
  html:
    toc: true
    page-layout: full
    include-after-body:
      text: |
        <script src="../assets/aos.js"></script>
        <script>
        AOS.init({
          anchorPlacement: 'top-left',
          duration: 1000,
          offset: 120
        });
        </script>
  typst:
    papersize: a4
    margin:
      x: 20mm
      y: 20mm
    include-in-header: cv.typ
  docx: default
css: ../assets/cv.css
format-links:
  - format: typst
    text: PDF
    icon: file-pdf
  - docx
---

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: load-libraries

library(httr2)
library(stringr)

cv_dir <- dirname(normalizePath(knitr::current_input(dir = TRUE)))
cv_data_dir <- file.path(cv_dir, "data")
source(file.path(cv_dir, "entries.R"))
```

```{r}
#| echo: false
#| results: asis
#| label: contact-details

render_contact()
```

## {{<fa briefcase>}} Appointments Held

```{r}
#| echo: false
#| results: asis

render_cv_entries("appointments.csv")
```

## {{<fa graduation-cap>}} Education

```{r}
#| echo: false
#| results: asis

render_cv_entries("education.csv")
```

## {{<fa book>}} Publications

```{r}
#| echo: false
#| results: asis
#| warning: false
#| message: false

req <- request("https://api.zotero.org") |>
  req_url_query(
    v = 3,
    include = "bib",
    sort = "date",
    style = "journal-of-ecology"
  ) |>
  req_url_path("users", "3027577", "publications", "items") |>
  req_retry()

zotero_api_key <- Sys.getenv("ZOTERO_API_KEY")
if (nzchar(zotero_api_key)) {
  req <- req |> req_headers(`Zotero-API-Key` = zotero_api_key)
}

decode_bibliography <- function(bibliography) {
  italic_open <- "QQQITALICOPENQQQ"
  italic_close <- "QQQITALICCLOSEQQQ"

  bibliography |>
    str_replace_all("<i>", italic_open) |>
    str_replace_all("</i>", italic_close) |>
    vapply(
      function(item) xml2::xml_text(xml2::read_html(paste0("<body>", item, "</body>"))),
      character(1)
    ) |>
    str_replace_all(italic_open, "*") |>
    str_replace_all(italic_close, "*")
}

resp <- req |> req_perform()

publications <- resp |>
  resp_body_json() |>
  purrr::map("bib") |>
  unlist() |>
  decode_bibliography() |>
  str_remove_all("\n") |>
  str_replace("(Lydeamore, M\\.( J\\.)?)", "**\\1**") |>
  str_replace_all("https?://[^\\s]+", function(url) paste0("<", url, ">")) |>
  str_trim()

preprints <- publications[str_count(publications, "medRxiv|arxiv|arXiv") > 0]
refereed <- publications[str_count(publications, "medRxiv|arxiv|arXiv") == 0]
```

### Preprints

```{r}
#| echo: false
#| results: asis

cat(paste0(" 1. ", preprints), sep = "\n\n")
```

### Peer-reviewed articles

```{r}
#| echo: false
#| results: asis

cat(paste0(" 1. ", refereed), sep = "\n\n")
```

## {{<fa money-bill>}} Funding

Almost all of this funding was obtained in partnership with large, collaborative teams.

```{r}
#| echo: false
#| results: asis

render_cv_entries("funding.csv")
```

## <i class="bi bi-chat-quote"></i> Conference presentations and contributed talks

```{r}
#| echo: false
#| results: asis

render_cv_entries("presentations.csv")
```

## {{<fa school>}} Teaching

```{r}
#| echo: false
#| results: asis

render_cv_entries("teaching.csv")
```

## {{<fa award>}} Awards

```{r}
#| echo: false
#| results: asis

render_cv_entries("awards.csv")
```

## {{<fa comments>}} Academic Service & Community Engagement

```{r}
#| echo: false
#| results: asis

render_cv_entries("service.csv")
```

**Reviewer**  
PLoS Computational Biology; Scientific Reports; Journal of Applied Mathematics; Journal of Statistical Software; Epidemiology & Infection; Mathematics; Medical Journal of Australia; International Tropical Health; Journal of Antimicrobial Resistance; The R Journal

## {{<fa users>}} Professional Memberships

```{r}
#| echo: false
#| results: asis

render_cv_entries("memberships.csv")
```
